Measurement and Probability in Fuzzy Quantum Theories

### 2017-05-22 prop_iop.tex
prop_letter.tex \subsection{From Interval-valued to Real-valued} Updating...

Previously we discussed how to construct a quantum IVPM from a quantum
real-valued probability measure; we then switch our focus to how to
construct a quantum real-valued probability measure from a special
kind of quantum IVPM.

\begin{definition}An interval-valued probability measure\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
is called $\delta$-deterministic if either $\left[l,r\right]\subseteq\left[0,\delta\right]$
or $\left[l,r\right]\subseteq\left[1-\delta,1\right]$ for every $\left[l,r\right]\in\mathscr{I}$.\end{definition}

For example, recall $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
then a $\mathscr{I}_{\mathrm{D}}$-valued QIVPM is $0$-deterministic.
For another example, given a three-dimensional Hilbert space, $\iota_{\frac{1}{3}}\circ\mu_{\frac{\mathbb{1}}{3}}^{\mathrm{B}}:\events\rightarrow\left\{ \imposs,\left[\frac{1}{3},\frac{1}{3}\right],\left[\frac{2}{3},\frac{2}{3}\right],\necess\right\} $
is a $\frac{1}{3}$-deterministic. However, we will prove there is
no $\delta$-deterministic probability measures for smaller $\delta$
due to the Kochen-Specker theorem.

@@

\begin{proof}~
\begin{itemize}
\item Since $\bar{\mu}(\mathbb{0})=\imposs$, we have $\mu(\mathbb{0})=0$.
\item Since $\bar{\mu}(\mathbb{1})=\necess$, we have $\mu(\mathbb{1})=1$.
\item For every event $P$, we have 
\begin{equation}\eqalign{ 
& \pmeas\left(P\right)=0\\ 
\Rightarrow & \bar{\mu}(P)\subseteq\left[0,\delta\right]\\
\Rightarrow & \bar{\mu}(\mathbb{1}-P)=\left[1,1\right]-\bar{\mu}(P)\subseteq\left[1-\delta,1\right]\\
\Rightarrow & \pmeas\left(\mathbb{1}-P\right)=1=1-\pmeas\left(P\right)\textrm{ .}
}\end{equation}
Similarly, when $\pmeas\left(P\right)=1$, we also have $\pmeas\left(\mathbb{1}-P\right)=1-\pmeas\left(P\right)$.
\item Given a collection $\left\{ P_{i}\right\} _{i=1}^{N}$ of pairwise
orthogonal events, we must have $N\le d$. Also, $\delta<\left(1+d\right)^{-1}\Rightarrow\delta\le d\delta<1-\delta$.
\begin{itemize}
\item If $\pmeas(P_{i})=0$ for all $i$, then
\begin{equation}\eqalign{ 
& \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})\subseteq\left[0,N\delta\right]\subseteq\left[0,d\delta\right]\\
\Rightarrow & \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\cap\left[1-\delta,1\right]=\textrm{Ø}\Rightarrow\bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\left[0,\delta\right]\\
\Rightarrow & \pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=0=\sum_{i=1}^{N}\pmeas(P_{i})\textrm{ .}
}\end{equation}
\item If $\pmeas\left(P_{i_{0}}\right)=1$ for a unique $i_{0}$, then
\begin{equation}\eqalign{ 
& \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})\subseteq\left[1-\delta,1+(N-1)\delta\right]\\
\Rightarrow & \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\cap\left[0,\delta\right]=\textrm{Ø}\Rightarrow\bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\left[1-\delta,1\right]\\
\Rightarrow & \pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=1=\sum_{i=1}^{N}\pmeas(P_{i})\textrm{ .}
}\end{equation}
\item If $\pmeas\left(P_{i_{0}}\right)=\pmeas\left(P_{i_{1}}\right)=1$
for $i_{0}\ne i_{1}$, then
\begin{equation}\eqalign{ 
& \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})\subseteq\left[2-2\delta,N\right]\\
\Rightarrow & \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\cap\left[0,\delta\right]=\bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\cap\left[1-\delta,1\right]\textrm{Ø}\textrm{ .}
}\end{equation}
A contradiction! Therefore, this case is impossible, and need no further
discussion.
\end{itemize}
\end{itemize}
\end{proof}

@@

\begin{cor}\label{cor:Kochen-Specker-IVPM}Given a Hilbert space
of dimension\nb$d\ge3$, there is no quantum $\delta$-deterministic
probability measure for $\delta<\left(1+d\right)^{-1}$. When $\delta\ge\left(1+d\right)^{-1}$,
there exists a quantum $\delta$-deterministic probability measure
$\bar{\mu}:\events\rightarrow\mathscr{I}$ for some $\mathscr{I}$.\end{cor}

\begin{proof}...\end{proof}

>>>>

Previously we discussed how to construct a quantum IVPM from a quantum
real-valued probability measure; we then switch our focus to how to
construct a quantum real-valued probability measure from a special
kind of quantum IVPMs.

\begin{definition}\label{def:delta-deterministic}An interval-valued
probability measure\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
is called $\delta$-deterministic if either $\left[l,r\right]\subseteq\left[0,\delta\right]$
or $\left[l,r\right]\subseteq\left[1-\delta,1\right]$ for every $\left[l,r\right]\in\mathscr{I}$.\end{definition}

Recall $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
so that a $\mathscr{I}_{\mathrm{D}}$-valued QIVPM is $0$-deterministic.
For another example, given a three-dimensional Hilbert space, $\iota_{\frac{1}{3}}\circ\mu_{\frac{\mathbb{1}}{3}}^{\mathrm{B}}:\events\rightarrow\left\{ \imposs,\left[\frac{1}{3},\frac{1}{3}\right],\left[\frac{2}{3},\frac{2}{3}\right],\necess\right\} $
is a $\frac{1}{3}$-deterministic. However, we will prove there is
no $\delta$-deterministic probability measures for small $\delta$
due to the Kochen-Specker theorem.

@@

\begin{proof}~
\begin{itemize}
\item Since $\bar{\mu}(\mathbb{0})=\imposs$, we have $\mu(\mathbb{0})=0$.
\item Since $\bar{\mu}(\mathbb{1})=\necess$, we have $\mu(\mathbb{1})=1$.
\item For every event $P$, we have 
\begin{equation}\eqalign{ 
& \pmeas\left(P\right)=0\Rightarrow\bar{\mu}(P)\subseteq\left[0,\delta\right]\\
\Rightarrow & \bar{\mu}(\mathbb{1}-P)=\left[1,1\right]-\bar{\mu}(P)\subseteq\left[1-\delta,1\right]\\
\Rightarrow & \pmeas\left(\mathbb{1}-P\right)=1=1-\pmeas\left(P\right)\textrm{ .}
}\end{equation}
Similarly, when $\pmeas\left(P\right)=1$, we also have $\pmeas\left(\mathbb{1}-P\right)=1-\pmeas\left(P\right)$.
\item Given a collection $\left\{ P_{i}\right\} _{i=1}^{N}$ of pairwise
orthogonal events, we must have $N\le d$. 
\begin{itemize}
\item If $\pmeas(P_{i})=0$ for all $i$, then
\begin{equation}\eqalign{ 
& \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})\subseteq\left[0,N\delta\right]\subseteq\left[0,d\delta\right]\\
\overset{d\delta<1-\delta}{\Rightarrow} & \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\cap\left[1-\delta,1\right]=\textrm{Ø}\Rightarrow\bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\left[0,\delta\right]\\
\Rightarrow & \pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=0=\sum_{i=1}^{N}\pmeas(P_{i})\textrm{ .}
}\end{equation}
\item If $\pmeas\left(P_{i_{0}}\right)=1$ for a unique $i_{0}$, then
\begin{equation}\eqalign{ 
& \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})\subseteq\left[1-\delta,1+(N-1)\delta\right]\\
\Rightarrow & \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\left[1-\delta,1\right]\Rightarrow\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=1=\sum_{i=1}^{N}\pmeas(P_{i})\textrm{ .}
}\end{equation}
\item If $\pmeas\left(P_{i_{0}}\right)=\pmeas\left(P_{i_{1}}\right)=1$
for $i_{0}\ne i_{1}$, then
\begin{equation}
\bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})\subseteq\left[2-2\delta,N\right]
\end{equation}
which contradicts to definition~\ref{def:delta-deterministic} so
that this case is impossible.
\end{itemize}
\end{itemize}
\end{proof}

@@

\begin{cor}\label{cor:Kochen-Specker-IVPM}Given a Hilbert space
of dimension\nb$d\ge3$, there is no quantum $\delta$-deterministic
probability measure for $\delta<\left(1+d\right)^{-1}$. \end{cor}
